\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{listings}
\usepackage{xcolor}

\lstset{
    basicstyle=\ttfamily\small,
    backgroundcolor=\color{gray!10},
    breaklines=true,
    frame=single
}

\begin{document}

\noindent
\textbf{\Large CS 352 Project 2: DNS Resolver - Wireshark Questions}\\[0.2cm]
\textbf{Name:} Your Name \hspace{2cm} \textbf{NetID:} your\_netid\\[0.5cm]

\section*{Part A: Recursive Resolver}

\textbf{Question 1:} What is the value of domain name found in the question section of the DNS query?

\begin{lstlisting}
05 69 6c 61 62 31 02 63 73 07 72 75 74 67 65 72 73 03 65 64 75 00
\end{lstlisting}

\vspace{0.3cm}

\textbf{Question 2:} What is the value of domain name found in the answer section of DNS response? Explain.

\begin{lstlisting}
c0 0c
\end{lstlisting}
This is a DNS compression pointer to offset 0x0C where the domain name appears in the question section.

\vspace{0.3cm}

\textbf{Question 3:} What is the value of the rdlength field in the DNS response message?

\begin{lstlisting}
00 04
\end{lstlisting}

\vspace{0.3cm}

\textbf{Question 4:} What is the value of the address received in the DNS response message?

\begin{lstlisting}
80 06 0d 02
\end{lstlisting}
IP address: 128.6.13.2

\vspace{0.5cm}

\section*{Part B: NS Records}

\textbf{Question 5:} What is the value of QDCOUNT, ANCOUNT, NSCOUNT, ARCOUNT in the DNS response message?

\begin{lstlisting}
QDCOUNT: 00 01
ANCOUNT: 00 02
NSCOUNT: 00 00
ARCOUNT: 00 00
\end{lstlisting}

\vspace{0.3cm}

\textbf{Question 6:} What is the value of the rdlength field in the DNS response message?

\begin{lstlisting}
Answer Record 1: 00 06
Answer Record 2: 00 08
\end{lstlisting}

\vspace{0.3cm}

\textbf{Question 7:} What are the name server names received in the response?

NS Record 1 (ns1.rutgers.edu):
\begin{lstlisting}
03 6e 73 31 c0 0f
\end{lstlisting}

NS Record 2 (runs2.rutgers.edu):
\begin{lstlisting}
05 72 75 6e 73 32 c0 0f
\end{lstlisting}

\vspace{0.5cm}

\section*{Part C: Iterative Resolver}

\textbf{Question 8:} What is the value of the type field in the first DNS query among the iterative messages?

\begin{lstlisting}
00 01
\end{lstlisting}

\vspace{0.3cm}

\textbf{Question 9:} What is the value of the type field value in resource records in first DNS response message among the iterative messages?

Authority Section:
\begin{lstlisting}
TYPE: 00 02 (NS records)
\end{lstlisting}

Additional Section:
\begin{lstlisting}
TYPE: 00 01 (A records)
TYPE: 00 1c (AAAA records)
\end{lstlisting}

\vspace{0.3cm}

\textbf{Question 10:} What is the destination IP of second DNS query sent? Where is this IP found from?

\begin{lstlisting}
c0 1f 50 1e
\end{lstlisting}
IP address: 192.31.80.30

This IP came from the Additional Records section (glue record) of the first DNS response from the root server (198.41.0.4). It is the A record for d.edu-servers.net.

\end{document}

